IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/extensions.tex
typo

Different concrete IFC implementations may wish to extend our minimal
system with labeled constructs appropriate for their envisioned
applications.
%
For example, SWAPI provides a labeled version of the XHR object, while
LIO implements a labeled file system, use in server-side web
applications~\cite{hails}.
%
Below we
consider the addition of several labeled constructs to the abstract specification.
%
We remark that that the non-interference proofs must account for the
new constructs, since they amend the IFC calculus semantics (usually
by addition).

>>>>

Different concrete IFC implementations may wish to extend our minimal
system with labeled constructs appropriate for their envisioned
applications.
%
For example, SWAPI provides a labeled version of the XHR object, while
LIO implements a labeled file system, used in server-side web
applications~\cite{hails}.
%
Below we
consider the addition of several labeled constructs to the abstract specification.
%
We remark that that the non-interference proofs must account for the
new constructs, since they amend the IFC calculus semantics (usually
by addition).
